Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-02-29 incidence-prevalence.tex
sort to dos, add a little more text

The infection process (\cref{inc-prev:sec:infection-process}) models how infections arise.
The concepts here are well-established within infectious disease epidemiology (see\todo{ref intro chapter}).

@@

\emph{Incidence} on day $t$, $Z_t$, is the number of people in a given population who become infected on day $t$; when expressed as a proportion of the population it is the \emph{incidence proportion}~\autocite[89]{lashModern}, $Z_t/\Npop$, where $\Npop$ is the number of people in the population.
As discussed in\todo{ref intro}, the timing of infection events is very rarely directly observable and must be inferred from other data.
Despite this issue, it remains the single most important quantity for informing the response to an epidemic or pandemic.

>>>>

The infection process (\cref{inc-prev:sec:infection-process}) models how infections arise.
The concepts here are well-established within infectious disease epidemiology.

@@

\emph{Incidence} on day $t$, $Z_t$, is the number of people in a given population who become infected on day $t$; when expressed as a proportion of the population it is the \emph{incidence proportion}~\autocite[89]{lashModern}, $Z_t/\Npop$, where $\Npop$ is the number of people in the population.
The timing of infection events is very rarely directly observable and must be inferred from other data.
Despite this issue, it remains the single most important quantity for informing the response to an epidemic or pandemic.

### 2024-02-29 introduction.tex
sort to dos, add a little more text

@@

Many mechanistic modelling studies were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.

@@

>>>>

\todo[inline]{Rewrite with more clarity backcalculation background: do I need the equation? What is it in practice? What did I write in my first-year report, and what comments did it get?}

@@

Many mechanistic modelling studies were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.
In the UK, the most influential were the outputs from SPI-M\todo{cite SPI-M and its outputs - Medley paper?}.
For example, the stages of lifting the lockdown in 2021 each had a set of modelling studies informing the government's decision\todo{cite roadmap 2021 papers}.

Each week, the members of SPI-M would produce a set of estimates of the current state of the epidemic (\eg ther value of $\Re$), known as \emph{nowcasting}.
These estimates, once any estimates unduly affected by issues (\eg data quality issues), were statistically combined into a consensus value.\todo{cite SPI-M combination}
The consensus value was published on \url{gov.uk} and informed the government's response to the epidemic.\todo{cite gov.uk R number}

The academic groups contributing estimates used a wide variety of methodologies

\todo[inline]{Finish lit review of SPI-M methods}

@@

\Textcite{colmanAscertainment} used CIS prevalence estiamtes to estimate the \emph{ascertainment rate} of community testing (the proportion of all infections that community testing detected).
Their methodology was similar to \textcite{abbottCISincidence}.
\Textcite{colmanAscertainment} do not require a Gaussian process (or other prior) to stabilise incidence estimates because they only estimate the ascertainment rate.
\todo[inline]{Finish writing about \textcite{colmanAscertainment}}
